Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Update Acknowledgements
Update Implications section

## Implications

### Implications for Methodology

@@

### Implications for Theory

This methodology should be of great interest to social scientists investigating social mobilization. It has potential applications for gender studies and the #MeToo movement, and for the relationship between social protest and repression during the Black Lives Matter protests. Fundamentally, this methodological approach can help us better understand the mechanisms underlying social media, and its influence on human behavior in real life. Given that many governments enact repressive measures when they determine that collective action by citizens has become an imminent possibility this methodology should help to improve the predictive power of using social media data in estimating repressive behavior. If social media messages are increasing in cohesion, this may represent a threat to civil and political liberties of citizens engaging in collective action.

@@

### Acknowledgements

>>>>

## Implications for Methodology and Theory

@@

This methodology should be of great interest to social scientists 
investigating social mobilization. It has potential applications for 
gender studies and the #MeToo movement and for the relationship between 
social protest and repression during the Black Lives Matter protests. 
Fundamentally, this methodological approach can help us better understand
the human social mechanisms underlying social media and its influence on human 
behavior in real life. Given that many governments enact repressive 
measures when they determine that collective action by citizens is
imminent, this methodology should help to improve 
the predictive power of using social media data in estimating repressive 
behavior. If social media messages are increasing in cohesion, this may 
represent a threat to civil and political liberties of citizens engaging
in collective action.

@@

# Acknowledgements

This work was completed in part as coursework done by lead author M. Chiovaro
in the ``Applications of Nonlinear Time Series Analysis'' graduate
course at the University of Connecticut (co-taught by coauthor A. Paxton and
Steven J. Harrison).
